---
title: "How to Publish to RPubs"
output:
  prettydoc::html_pretty:
    theme: cayman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# R Markdown
Great for creating beautiful reports with a mix of text/notes and code. R Markdown files can also be easily converted to html, pdf, or word docs

# Insert code
```{r}
library(tidyverse)
library(palmerpenguins)
library(ggeasy)

gentoo <- penguins %>%
  filter(species == "Gentoo") %>%
  na.omit()

ggplot(gentoo, aes(x=bill_length_mm, y=body_mass_g)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Relationship between bill length \nand body mass of Gentoo penguins",
       x = "Bill Length (mm)",
       y = "Body Mass") +
  easy_text_size(20)
```

# Knit for Preview

# Pretty RMarkdown formats
- [prettydoc](https://github.com/yixuan/prettydoc)
```{r eval = FALSE}
# add this to your YAML
output:
  prettydoc::html_pretty:
    theme: cayman
```

- [rmdformats](https://github.com/juba/rmdformats)
```{r eval = FALSE}
# add this to your YAML
output: rmdformats::readthedown
```

# How to publish to RPubs?

1. After you've knit your document, in the viewer pane click the blue icon in the top right corner
2. Click publish to RPubs and publish!
3. Provide title and URL 